%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%     File: Thesis_Acknowledgments.tex                                 %
%     Tex Master: Thesis.tex                                           %
%                                                                      %
%     Author: Andre C. Marta                                           %
%     Last modified :  2 Jul 2015                                      %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{\acknowledgments}

% Add entry in the table of contents as section
\addcontentsline{toc}{section}{\acknowledgments}

I want to thank the Instituto Superior Técnico and CENTRA for giving me the opportunity to carry out my work and for allowing me to continue satisfying my curiosity for physics. To my supervisor, Edgar, for being the person who supported me the most, guided me, listened to me, and helped me through all my existential crises. His infinite patience and availability to meet with me at any time are truly appreciated. \\
To my co-supervisor, Alex, for his commitment and dedication in helping me solve all the issues related to GitHub, for teaching me how to use Mathematica, and above all, for sharing with me the same passion and love for relativity that he had. \\
To all my friends, thank you for supporting and encouraging me to continue on this path. To Diogo, for welcoming me into his office and creating a harmonious space where joy and good humor reigned every day, for the various topics of conversation, and for all the help he provided. \\
To Ricardo, for everything he has done for me, for being a constant presence during these two years, for always helping me with any technological and computational problems, for his humility, selflessness, and friendship. \\
To my girlfriend, Daniela, for all the love, care, and support she has given me throughout my journey, for helping me solve problems with her unique perspective, and for believing in me, even when I doubted myself. \\
To my parents, for providing me with all the necessary tools and teachings that allowed me to reach where I am today and become who I am. Without them, none of this would have been possible. Thank you for all the help you have given me and everything you have done for me. I love you both very much.

